---
title: "p8105_hw5_yq2378"
author: "Qi Yumeng"
date: "2023-11-12"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, load libraries}
library(tidyverse)
library(ggpubr)
```
# Problem 1 

```{r, load p1 data}
# loading data
homicide = read.csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv")
```

```{r, ttl homicide data by city}
homicide = homicide %>% 
  mutate(city_state = str_c(city, state, sep=", ")) 
ttl_bycity = homicide %>% 
  mutate(if_solved = if_else(disposition == "Closed by arrest",1,0 )) %>% 
  group_by(city) %>% summarise( ttl_cnt = n(), unsolved_cnt = n() - sum(if_solved), .groups = "keep") %>%
  arrange(desc(ttl_cnt)) 
ttl_bycity
```

For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe

```{r, Baltimore case}
ttl_cnt = 2827
unsolved_cnt = 1825
prop_output = prop.test(x = unsolved_cnt, n = ttl_cnt)
broom::tidy(prop_output)
broom::tidy(prop_output) %>% pull(estimate)
broom::tidy(prop_output) %>% pull(conf.low, conf.high)
```

```{r, iteration}
CI_bycity = 
  ttl_bycity |>
  mutate(prop_output = map2(.x = unsolved_cnt, .y = ttl_cnt, prop.test),
         prop_output = map(prop_output,broom::tidy)) |> 
  unnest(prop_output) |>
  mutate(CI = paste("(",round(conf.low,4),", ", round(conf.high,4),")"),
         estimate = round(estimate, 4)) |>
  select(city, ttl_cnt, unsolved_cnt, estimate,CI, conf.low, conf.high)
CI_bycity
```

```{r, error_bar}
CI_bycity |>
  ggplot(aes(x = factor(city), y = estimate))+ 
  geom_point(size = 0.8) + 
  geom_errorbar(aes(ymin = conf.low,  ymax = conf.high), width = 0.2) + 
  coord_flip() + 
  theme_pubr() + xlab("City") + ylab("Estimate the Proportion of unsolved homicides") +
  theme(text = element_text(size = 8),
        plot.margin = unit(c(.1,.1,.1,.1),'cm'))

```
# Problem 2

This zip file contains data from a longitudinal study that included a control arm and an experimental arm. Data for each participant is included in a separate file, and file names include the subject ID and arm.

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

Start with a dataframe containing all file names; the list.files function will help
Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups

```{r,load p2 data}
file_name = list.files(path = "./data")
file_name = paste("./data/",file_name, sep="")
study = tibble(
  arm = substr(file_name,8,10),
  subject_id = substr(file_name,12,13)) |>
  mutate(table = map(file_name, read.csv)) |>
  unnest(cols = "table") |>
  pivot_longer(cols = starts_with("week_"),
               names_to = "week",
               values_to = "values") |>
  mutate(week = substr(week, 6,6),
         week = as.numeric(week),
         arm = if_else(arm == "exp","experimental","control"),)
study
```

```{r,spaghetti PLOT!}
ggplot(data = study, aes(x = week, y = values, color = subject_id, linetype = arm)) +
  #geom_line(aes(subject_id), linewidth = 1) +
  geom_line(linewidth = 0.5)+
  theme_pubr(legend = "right") +
  labs(x = "Week Time", y = "Value") 
```